Why Donors Donate?

### 2020-09-09 analysis/05_market_simulator.Rmd
In process of finishing Persona Inputs

# Need to Fix
selectInput("p1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("0", '1', '2', '3','4','5','6','7'))

selectInput("p1_donation_frequency",
         label = "Donation Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years',
                     'Never'))

# Need to Fix
selectInput("p1_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

selectInput("p1_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("Volunteered", "Not Volunteered"))

# Need to Fix
selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c('Once a week',
                     'Once a Month',
                     'Once every three months',
                     'Once every six months',
                     'Once a year',
                     'Once every few years'))

# Need to Fix
selectInput("p1_personal_activism",
         label = "Personal Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

# Need to Fix
selectInput("p1_family_activism",
         label = "Family Activism:",
         choices = c('Extremely involved',
                     'Very involved',
                     'Moderately involved',
                     'Slightly involved',
                     'Never involved'))

# Need to Fix
selectInput("p1_religious_member",
         label = "Church Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_labor_member",
         label = "Labor Union Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_political_member",
         label = "Political Party Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_professional_member",
         label = "Professional Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

# Need to Fix
selectInput("p1_other_member",
         label = "Other Org. Membership:",
         choices = c('Active Member',
                     'Inactive Member',
                     "Don't belong"))

@@

# Need to Fix
selectInput("p1_education",
         label = "Education:",
         choices = c("Less than Highschool",
                     "Highschool Graduate",
                     "Some College",
                     "2 Year College",
                     "4 Year College",
                     "Graduate or Professional Degree",
                     "Doctorate"))
# Need to Fix
selectInput("p1_income",
         label = "Income:",
         choices = c('Less than $10,000',
                     '$10,000 to $19,999',
                     '$20,000 to $29,999',
                     '$30,000 to $39,999',
                     '$40,000 to $49,999',
                     '$50,000 to $59,999',
                     '$60,000 to $69,999',
                     '$70,000 to $79,999',
                     '$80,000 to $89,999',
                     '$90,000 to $99,999',
                     '$100,000 to $149,999',
                     '$150,000 to $199,999',
                     '$200,000 to $299,999',
                     '$300,000 or more'))

>>>>

# Need to Fix
selectInput("p1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("Very little Trust"))

# Double Check this one
selectInput("p1_donation_frequency",
         label = "Donation Frequency:",
         choices = c('Rarely',
                     'Atleast once a month'))

selectInput("p1_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'))

# Need to Change the Inputs
selectInput("p1_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("No", "Yes"))

# Need to Fix
selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't Volunteered",
                     "Rarely",
                     "More than once a month, less than once a year",
                     "At least once a month"))

# Need to Fix
selectInput("p1_personal_activism",
         label = "Personal Activism:",
         choices = c('Not Involved',
                     'Involved'))

# Need to Fix
selectInput("p1_family_activism",
         label = "Family Activism:",
         choices = c('Not Involved',
                     'Involved'))

# Need to Fix
selectInput("p1_religious_member",
         label = "Church Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_labor_member",
         label = "Labor Union Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_political_member",
         label = "Political Party Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_environmental_member",
         label = "Enviornmental Org. Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_professional_member",
         label = "Professional Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

# Need to Fix
selectInput("p1_other_member",
         label = "Other Org. Membership:",
         choices = c("Don't belong",
                     'Inactive Member',
                     'Active Member'))

@@

# Need to Fix
selectInput("p1_education",
         label = "Education:",
         choices = c("Less than Highschool",
                     "Highschool Graduate",
                     "Some College",
                     "2 Year College",
                     "4 Year College",
                     "Graduate or Professional Degree",
                     "Doctorate"))
# Need to Fix
selectInput("p1_income",
         label = "Income:",
         choices = c('Less than $10,000',
                     'More than Median (>$61,372)'))
